Projekt Medieninformatik\\Facial Expresson Recognition\\ Using A State Of The Art CNN

### 2018-02-22 doc/doc.tex
new paper

        \section{Abstract}
            Automatically recognizing facial expressions is an interesting and challenging problem in many fields, including human computer interaction (HCI).
            The projects goal is to build a device to process live webcam
            images, detect faces and classify the emotion of each face.
            In order to get started with deep learning techniques and state 
            of the art neural networks, I am participating in a Facial 
            Expression Recognition 
            Challenge\footnote{https://www.kaggle.com/c/challenges-in-representation-learning-facial-expression-recognition-challenge/data} 
            on Kaggle.

>>>>

        \section{Introduction}
            Automatically recognizing facial expressions is an interesting and challenging problem in many fields, including human computer interaction (HCI) and artificial emotional intelligence.
            The projects goal is to build a device to process live webcam
            images, detect faces and classify the emotion of each face.
            In order to get started with deep learning techniques and state 
            of the art neural networks, I am participating in a Facial 
            Expression Recognition 
            Challenge\footnote{https://www.kaggle.com/c/challenges-in-representation-learning-facial-expression-recognition-challenge/data} 
            on Kaggle.
